Continuous Deployment and Schema Evolution \\in SQL Databases

### 2015-01-23 paper.tex
Removed some unnecessary commas.

\section{Road ahead}
As stated before, work on QuantumDB is not finished. To be able to use QuantumDB effectively in production environments, we still need to work on the following issues:

\begin{itemize}
  \item{QuantumDB can already deal with foreign keys referring from tables under change to other tables not under change. To fully support foreign keys QuantumDB would also need to be able to handle foreign keys referring to tables under change. This is currently being worked on.}
  \item{Use performance metrics to throttle the copy phase. When the database is (too) busy, (high disk I/O, high CPU usage, or memory starvation), we should slow down the iterative copy process. Vice-versa we can speed it up when the database is not under load.}
  \item{QuantumDB currently only supports PostgreSQL, but since most SQL databases have support for triggers and procedures of some kind, this should prove easily extendable to other popular SQL databases.}
  \item{The driver currently uses a very rudimentary query rewriting algorithm to replace table names under change with the names of ghost tables. It does not yet support the entire PostgreSQL query syntax.}
\end{itemize}

>>>>

\section{Road ahead}
As stated before, work on QuantumDB is not finished. To be able to use QuantumDB effectively in production environments we still need to work on the following issues:

\begin{itemize}
  \item{QuantumDB can already deal with foreign keys referring from tables under change to other tables not under change. To fully support foreign keys QuantumDB would also need to be able to handle foreign keys referring to tables under change. This is currently being worked on.}
  \item{Use performance metrics to throttle the copy phase. When the database is (too) busy (high disk I/O, high CPU usage, or memory starvation), we should slow down the iterative copy process. Vice-versa we can speed it up when the database is not under load.}
  \item{QuantumDB currently only supports PostgreSQL, but since most SQL databases have support for triggers and procedures of some kind, this should prove easily extendable to other popular SQL databases.}
  \item{The driver currently uses a very rudimentary query rewriting algorithm to replace table names under change with the names of ghost tables. It does not yet support the entire PostgreSQL query syntax.}
\end{itemize}
